\dppTitle

### 2014-03-06 manuscripts/dpp-msbayes/dpp-msbayes-main.tex
Reverting bib management in dpp ms.
Reverting back to natbib bib management for dpp ms.
Reverting back to numerical citations for dpp ms.
Reverting back to the use of `cite` in place of `citep` and `citep` for
dpp ms.

Changes were made in:
    `dpp-msbayes-main.tex`
    `dpp-msbayes-tables.tex`
    `../utils/macros.tex`
Updating main text of dpp ms.
Updating the section titles and adding a conclusions section to
`dpp-msbayes-main.tex`.

\section{Introduction}

@@

The second prior is based on the Dirichlet process, which is a stochastic
process that groups random variables into an unknown number of discrete
parameter classes \cite{Ferguson1973,Antoniak1974}.
The Dirichlet process has been used as a nonparametric Bayesian approach to
many inference problems in evolutionary biology
\cite{Lartillot2004,Huelsenbeck2007,HuelsenbeckSuchard2007,Ane2007,Heath2011,Heath2012}.
Here, I use the Dirichlet process to place a prior over all possible ordered
partitions of \npairs{} population pairs into divergence-time parameter classes
(i.e., ``divergence events'').
As discussed above, the time of each divergence-time parameter is drawn from
the base distribution $\divTime{} \sim Gamma(\gammaShape{\divTime{}},
\gammaScale{\divTime{}})$.
The partitioning of the population pairs to divergence-time classes is
controlled by the concentration parameter \concentrationParam, which determines
how clustered the process will be.
I take a hierarchical approach and use a prior probability
distribution (i.e., hyperprior) for \concentrationParam \cite{Escobar1995}.
More specifically, I use a gamma-distributed prior $\concentrationParam \sim
Gamma(\gammaShape{\concentrationParam}, \gammaScale{\concentrationParam})$,
where \gammaShape{\concentrationParam} and \gammaScale{\concentrationParam} are
specified by the investigator.
I use $\divTimeIndexVector \sim \priorDPP{}$ to denote this Dirichlet-process
prior.

@@

>>>>

% \section{Introduction}
\section{Background}

@@

The second prior is based on the Dirichlet process, which is a stochastic
process that groups random variables into an unknown number of discrete
parameter classes \cite{Ferguson1973,Antoniak1974}.
The Dirichlet process has been used as a non-parametric Bayesian approach to
many inference problems in evolutionary biology
\cite{Lartillot2004,Huelsenbeck2007,HuelsenbeckSuchard2007,Ane2007,Heath2011,Heath2012}.
Here, I use the Dirichlet process to place a prior over all possible ordered
partitions of \npairs{} population pairs into divergence-time parameter classes
(i.e., ``divergence events'').
As discussed above, the time of each divergence-time parameter is drawn from
the base distribution $\divTime{} \sim Gamma(\gammaShape{\divTime{}},
\gammaScale{\divTime{}})$.
The partitioning of the population pairs to divergence-time classes is
controlled by the concentration parameter \concentrationParam, which determines
how clustered the process will be.
I take a hierarchical approach and use a prior probability
distribution (i.e., hyperprior) for \concentrationParam \cite{Escobar1995}.
More specifically, I use a gamma-distributed prior $\concentrationParam \sim
Gamma(\gammaShape{\concentrationParam}, \gammaScale{\concentrationParam})$,
where \gammaShape{\concentrationParam} and \gammaScale{\concentrationParam} are
specified by the investigator.
I use $\divTimeIndexVector \sim \priorDPP{}$ to denote this Dirichlet-process
prior.

@@

\section{Conclusions}
I introduced a new approximate-Bayesian model-choice method for estimating
shared divergence histories across taxa using DNA sequence data.
The new method, \dppmsbayes, takes a non-parametric approach to the problem by
using a Dirichlet-process prior on the temporal distribution of divergences
across taxa.
The new method shows improved robustness, accuracy, and power compared to the
existing method, \msb.
Compared to \msb, the new approach better estimates posterior uncertainty,
which greatly reduces the chances of incorrectly estimating biogeographically
interesting scenarios of shared divergence events.
This new tool will allow evolutionary biologists to better leverage comparative
genetic data to assess the affects of regional and global biogeographical
processes on biodiversity.
